Tracing the Hercules stream around the Galaxy

### 2010-05-19 tex/hercules.tex
groups-simulations: abstract

\begin{abstract}
%Various dynamical scenarios related to the Milky Way's bar or spiral
%structure have been proposed to explain the existence of moving
%groups---clumps of co-moving stars---in the Solar neighborhood. Since
%the observed pattern of moving groups is very sensitive to the
%properties of the non-axisymmetric feature that creates them, these
%moving groups can be a powerful tool in constraining the dynamical
%structure of the inner Milky Way. However, at present the various
%models are hard to confirm and distinguish with observations of the
%local Galactic neighborhood. We show that future programs that survey
%the Milky Way disk's kinematics on a more global scale can distinguish
%between these models. By integrating orbits of stars in various
%steady-state and transient bar and spiral structure potentials that
%produce the pattern of moving groups observed in the Solar
%neighborhood, we predict the velocity distribution as a function of
%location in the Galactic disk. We identify the locations that
%distinguish most clearly between the various scenarios. Future
%infrared radial velocity surveys can probe the velocity distribution
%at these locations. We predict the distribution of radial velocities
%that can be directly compared to observations to establish the origin
%of the moving groups and to constrain the structural and dynamical
%parameters of the non-axisymmetric Milky Way potential.
\end{abstract}

\keywords{
  Galaxy: bulge
  ---  
  Galaxy: disk
  ---
  Galaxy: evolution
  ---
  Galaxy: fundamental parameters
  ---
  Galaxy: kinematics and dynamics
  ---
  Galaxy: structure
}

>>>>

\begin{abstract}
It has been proposed that the Hercules stream, a group of co-moving
stars in the Solar neighborhood offset from the bulk of the velocity
distribution, is the result of resonant interactions between stars in
the outer disk and the Galactic bar. Only seen so far in the immediate
Solar neighborhood, I predict the distribution of stellar velocities
and the run of the Hercules stream as a function of location in the
Galactic disk in a simple model for the Galaxy and the bar that
produces the observed Hercules stream. I further show that the
Hercules feature is strong enough that it can be unambiguously
detected in the distribution of line-of-sight velocities in selected
directions. I quantify the most promising lines-of-sight for the
detection of the Hercules stream in radial velocities: The most
promising directions to target are at $l \geq 250^{\circ}$. The
predictions presented here are only weakly affected by distance
uncertainties, assumptions about the distribution function of the old
stellar disk, and the details of the Galactic potential including the
effect of spiral structure; \Gaia\ and future spectroscopic surveys of
the Galactic disk will be able to robustly test the origin of the
Hercules stream and constrain the properties of the Galactic bar.
\end{abstract}

\keywords{Galaxy: bulge --- Galaxy: disk --- Galaxy: evolution ---
  Galaxy: fundamental parameters --- Galaxy: kinematics and dynamics
  --- Galaxy: structure }
